Chemistry of fossil Pinus pollen and the effect of acetolysis

### 2021-04-12 manuscript.Rmd
wrote plotting functions and plots of mean spectra; moved outlier removal into manuscript data loading code

\newpage
<!-- READ DATA -->
```{r}
source(here("R","ages.R"))
if (file.exists(here("data","output","DAL_spectra.rds"))) {
  DAL = readRDS(here("data","output","DAL_spectra.rds"))
} else {
  source(here("R","read_data.R"))
  read_data("DAL")
  DAL = readRDS(here("data","output","DAL_spectra.rds"))
}

@@

FRE$Label = "FRE"
DAL$Label = "DAL"
TSK$Label = "TSK"
MFM$Label = "MFM"
```

@@

>>>>

\newpage
<!-- READ DATA -->
```{r}
source(here("R","ages.R"))
if (file.exists(here("data","output","DAL_spectra.rds"))) {
  DAL = readRDS(here("data","output","DAL_spectra.rds"))
  DAL$age = 0
} else {
  source(here("R","read_data.R"))
  read_data("DAL")
  DAL = readRDS(here("data","output","DAL_spectra.rds"))
}

@@

FRE$Label = "FRE"
DAL$Label = "DAL"
TSK$Label = "TSK"
MFM$Label = "MFM"

outliers = c("DAL_rx1GZ", "DAL_2cxp7", "DAL_VzFi0", "DAL_ANdP0", "MFM_av67v", "MFM_OftM2", "MFM_xogJr", "MFM_hoG4y", "MFM_5UNIJ", "TSK_vvgOZ", "DAL_xgYjM", "TSK_m4hN6", "TSK_e04Go")

DAL = DAL[!DAL$ids %in% outliers,]
TSK = TSK[!TSK$ids %in% outliers,]
MFM = MFM[!MFM$ids %in% outliers,]
```

@@

# Results

```{r echo=FALSE, fig.cap="FRE", message=FALSE, warning=FALSE, out.width="100%"}
mean_plots = readRDS(here("data","output","mean_plots.rds"))

mean_plots[[7]]
```

```{r echo = FALSE, message=FALSE, warning=FALSE, out.width = "100%", fig.cap="DAL SPT"}
mean_plots[[1]]
```

```{r echo = FALSE, message=FALSE, warning=FALSE, out.width = "100%", fig.cap="DAL acet"}
mean_plots[[2]]
```

```{r echo = FALSE, message=FALSE, warning=FALSE, out.width = "100%", fig.cap="TSK SPT"}
mean_plots[[3]]
```

```{r echo = FALSE, message=FALSE, warning=FALSE, out.width = "100%", fig.cap="TSK acet"}
mean_plots[[4]]
```

```{r echo = FALSE, message=FALSE, warning=FALSE, out.width = "100%", fig.cap="MFM SPT"}
mean_plots[[5]]
```

```{r echo = FALSE, message=FALSE, warning=FALSE, out.width = "100%", fig.cap="MFM acet"}
mean_plots[[6]]
```

```{r echo = FALSE, message=FALSE, warning=FALSE, out.width = "100%", fig.cap="DAL SPT"}
blank_mean_plots = readRDS(here("data","output","blank_mean_plots.rds"))
blank_mean_plots[[1]]
```

```{r echo = FALSE, message=FALSE, warning=FALSE, out.width = "100%", fig.cap="DAL acet"}
blank_mean_plots[[2]]
```

```{r echo = FALSE, message=FALSE, warning=FALSE, out.width = "100%", fig.cap="TSK SPT"}
blank_mean_plots[[3]]
```

```{r echo = FALSE, message=FALSE, warning=FALSE, out.width = "100%", fig.cap="TSK acet"}
blank_mean_plots[[4]]
```

```{r echo = FALSE, message=FALSE, warning=FALSE, out.width = "100%", fig.cap="MFM SPT"}
blank_mean_plots[[5]]
```

```{r echo = FALSE, message=FALSE, warning=FALSE, out.width = "100%", fig.cap="MFM acet"}
blank_mean_plots[[6]]
```
